---
title: "ACTL90020 Module 7"
output: html_notebook
---

### This notebook is for the module 7 exercises of ACTL90020

**7.2 Examples**

```{r 7.2.1 Prep}
library(astsa) # Applied Statistical TS Analysis
library(xts) # eXtensible TS
library(quantmod)

DJI = getSymbols("^DJI", src="yahoo",
                 from="2006-01-01", to="2020-12-31", periodicity="daily",
                 env=NULL)

ASX200 = getSymbols("^AXJO", src="yahoo", 
                    from="2006-01-01", to="2020-12-31", periodicity="daily",
                    env=NULL)

ASX200 = na.approx(ASX200)

ASX200.high = ASX200$AXJO.High
DJI.high = DJI$DJI.High
```

```{r 7.2.1, echo=F}
plot(ASX200.high)
plot(DJI.high)
```

*7.2.2: Using 21-point centered MA*
```{r 7.2.2, echo=F}
# 7.2.2
# 21-point MA

ASX.21MA = filter(ASX200.high, filter=rep(1/42, 42), sides=2)
DJI.21MA = filter(DJI.high, filter=rep(1/42, 42), sides=2)

plot(ASX.21MA)
plot(DJI.21MA)
```

**7.3 Describing the behaviour of basic models**

*7.3.1*

Calculate the autocovariance and autocorrelation of MA(1):  

$$ x_t = \mu + w_t + \beta_1 w_{t-1} $$

*Autocovariance*
\begin{align}
    \gamma (s, t) &= E[(x_t - \mu_t)(x_s - \mu_s)] \\
    &= E[(w_t + \beta_1 w_{t-1})(w_s + \beta_1 w_{s-1})] \\
    &= \begin{cases}
            (1+\beta_1^2)\sigma_w^2 & \text{if $t=s$} \\
            \beta_1 \sigma_w^2 & \text{if $|t-s|=1$} \\
            0 & \text{Otherwise} 
        \end{cases}
\end{align}

*Autocorrelation*  

$$\rho (s, t) = \begin{cases}
    1 & \text{if $t=s$} \\
    \frac{\beta_1}{1+\beta_1^2} & \text{if $|t-s|=1$} \\
    0 & \text{Otherwise}
\end{cases} $$

*7.3.2*
*For MA(2)*
$$\rho (s, t) = \begin{cases}
    1 & \text{if $t=s$} \\
    \frac{\beta_1 + \beta_1 \beta_2}{1+\beta_1^2 + \beta_2^2} & \text{if $|t-s|=1$} \\
    \frac{\beta_2}{1+\beta_1^2 + \beta_2^2} & \text{if $|t-s|=2$} \\
    0 & \text{Otherwise}
\end{cases} $$


The ACF for when $(\beta_1 = 0.3, \beta_2 = -0.4)$ and $(\beta_1 = -1.2, \beta_2 = -1.6)$ are the same.

*7.3.3*
```{r 7.3.3 Simulation}
set.seed(10)

q = 5
sigma = 5

N=500
n=10

tot.res = rep(0, n+1)

for (i in 1:1000) {
    w_t = rnorm(N, 0, sd=sqrt(sigma))
    v_t = filter(w_t, filter = rep(1/(2*q+1), 2*q+1), method="convolution", sides=2)
    v_t = na.omit(v_t)
    
    empirical.ACF = acf(v_t, lag.max=n, type="covariance", plot=F)$acf
    theoretical.ACF = (sigma/(2*q+1)^2)*seq(from=2*q+1, to=2*q+1-n)
    
    res = empirical.ACF - theoretical.ACF
    
    tot.res = tot.res + res
}

print(as.vector(tot.res/1000))
```












